How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
Explanation for the use of term procedures

\subsubsection{Custom Blocks}
Scratch users can define their own blocks, which users can name themselves, called custom blocks. To align with other papers on this topic \todo{Fenia, a reference?} we will refer to them as `procedures' in the following. Procedures can have input parameters of type string, number, and boolean. When a user defines a procedure, a new Hat block called \texttt{define} appears, which users can fill with the implementation of their block.

@@

\subsubsection{Dead Code}
In our analysis, we find that almost one quarter of the Scratch projects contain dead `scripts': scripts that are never invoked due to the lack of a starting \texttt{when <trigger>} block from the Scratch Events or Control category, like in the example in Figure \ref{fig:Unconnected_clones}, or scripts that are comprised of only a \texttt{when <trigger>} block without any functionality. \todo{Fenia, this is correct, right, the 23\% is just these types and not also uncalled procs and unmatched broadcasts?}.

>>>>

\subsubsection{Custom Blocks}
Scratch users can define their own blocks, which users can name themselves, called custom blocks. The creation of custom blocks in Scratch is the equivalent of defining procedures in other languages \cite{moreno_automatic_2014}. Because the term `procedures' is common in the software engineering area, for readability we will refer to custom blocks as `procedures' in the following. Procedures can have input parameters of type string, number, and boolean. When a user defines a procedure, a new Hat block called \texttt{define} appears, which users can fill with the implementation of their block.

@@

\subsubsection{Dead Code}
In our analysis, we find that more than one quarter of the Scratch projects contain dead `scripts': scripts that are never invoked due to the lack of a starting \texttt{when <trigger>} block from the Scratch Events or Control category, scripts that are comprised of only a \texttt{when <trigger>} block without any functionality, procedures that are not invoked, or unmatched broadcast-receive messages.
